DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-10-23 scnn.tex
remove todolist

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
    \item (TK) check part sphere notebook and whole sphere
	\item (NP \& MD) Move the git repository, rename the classes, check the links.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

>>>>

% \section*{TODO list}
% \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
% 	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
% 	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
% 	\item (TK) Check use of British vs American English. Check use of tense.
% 	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
%     \item (TK) check part sphere notebook and whole sphere
% 	\item (NP \& MD) Move the git repository, rename the classes, check the links.
%     \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
% 	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
% \end{itemize}
